Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-15 05_calibration_data.Rmd
add ref to christine and link to data
add note on dt syntx

Here we show how the residence patch method [@barraquand2008; @bijleveld2016; @oudman2018] accurately estimates the duration of known stops in a track collected as part of a calibration exercise in the Wadden Sea.

@@

@@

First we access the data from a local file using the `data.table` package [@dowle2020].
We then visualise the raw data.

```{r}
# read and plot example data
data <- fread("data/atlas1060_allTrials_annotated.csv")
data_raw <- copy(data)
```

>>>>

Here we show how the residence patch method [@barraquand2008; @bijleveld2016; @oudman2018] accurately estimates the duration of known stops in a track collected as part of a calibration exercise in the Wadden Sea. These data can be accessed from the `data` folder at this link: https://doi.org/10.5281/zenodo.4287462. These data are more fully reported in [@beardsworth2021].

@@

### A Note on `:=` {-}

The `atlastools` package is based on `data.table`, to be fast and efficient [@dowle2020].
A key feature is modification in place, where data is changed without making a copy.
This is already implemented in `R` and will be familiar to many users as `data_frame$column_name <- values`.

The `data.table` way of writing this assignment would be `data_frame[, column_name := values]`.
We use this syntax throughout, as it provides many useful shortcuts, such as multiple assignment:

`data_frame[, c("col_a", "col_b) := list(values_a, values_b)]`

Users can use this special syntax, and will find it convenient with practice, but there are _no_ cases where users _must_ use the `data.table` syntax, and can simply treat the data as a regular `data.frame`. However, users are advised to convert their `data.frame` to a `data.table` using the function `data.table::setDT()`.

@@

First we access the data from a local file using the `data.table` package [@dowle2020].
We look at the first few rows, using `head()`.
We then visualise the raw data.

```{r}
# read and plot example data
data <- fread("data/atlas1060_allTrials_annotated.csv")
data_raw <- copy(data)

# see raw data
head(data_raw)
```
